Reproducible Research in R: A Tutorial on how to Do the Same Thing More Than Once

### 2021-11-16 manuscript.Rmd
refine tutorial scope closes #278

This tutorial assumes that the user is predominantly working in R, with the help of RStudio.
It describes basic steps that we expect to be representative of a small-scale psychological research project. 
Of course, your specific situation might involve additional, more specialized steps. 
After completing the tutorial, you should be able to customize your workflow accordingly.

>>>>

This tutorial assumes that the user is predominantly working in R, with the help of RStudio.
It describes basic steps that we expect to be representative of a small-scale psychological research project that relies on no external software or multistage data processing (for those requirements see section [Advanced Features]). 
Of course, your specific situation might involve additional, more specialized steps. 
After completing the tutorial, you should be able to customize your workflow accordingly.
